%-------------------------
% Author : Paul Hondola
% License : MIT
%------------------------

\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large }{}{0em}{}[
\color{black}
\titlerule
\vspace{-5pt}
]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{ \item\small{ {#1 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}
\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
	\textbf{#1}       & #2                 \\
	\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}
\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{ \item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
	\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}
\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{ \item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
	\small#1 & #2 \\
\end{tabular*}
\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}
\vspace{-4pt}}

\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}
\vspace{-5pt}}

\begin{document}
	%----------HEADING----------

	\begin{center}
		\textbf{\Huge \scshape Paul Hondola} \\
		\vspace{1pt}
		\small +40745166873 $|$ \href{mailto:paulhondola@gmail.com}{\underline{paulhondola@gmail.com}}
		$|$ \href{https://linkedin.com/in/paulhondola}{\underline{linkedin.com/in/paulhondola}} $|$
		\href{https://github.com/paulhondola}{\underline{github.com/paulhondola}}
	\end{center}

	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart

	\resumeSubheading{Bachelor of Science in Computer Engineering}{Oct. 2023 -- Jun. 2027}{Universitatea Politehnica Timisoara}{}
	\resumeItemListStart
		\resumeItem{Relevant Coursework: Data Structures and Algorithms, Operating Systems, Computer Architecture, Distributed Systems, Networking, Web Development.}
	\resumeItemListEnd

	\resumeSubHeadingListEnd

	%-----------EXPERIENCE-----------
	\section{Experience}
	\resumeSubHeadingListStart

	\resumeSubheading {Software Engineer Intern}{Mar. 2026 -- Present} {Nokia $|$ \emph{Python, Jenkins, Docker, Power BI}}{}
    \resumeItemListStart
        \resumeItem{Profiled and optimized data-processing Python scripts, reducing end-to-end runtime by 50\% through algorithmic refactoring and numpy vectorization.}
        \resumeItem{Contributed to the Mobile Infrastructure Metrics Automation platform, developing ETL scripts and automated test pipelines for various analytics.}
		\resumeItem{Enhanced CI/CD pipelines using Jenkins and Docker for scalable metric processing and analysis.}
		\resumeItem{Maintained and improved interactive Power BI dashboards to surface key metrics and KPIs.}
		\resumeItem{Contributed reusable modules to the team's shared core library, extending common functionality leveraged across multiple internal automation projects.}
    \resumeItemListEnd

    \resumeSubheading {Full Stack Developer Intern}{Jul. 2025 -- Oct. 2025} {Hibyte $|$ \emph{Typescript, Angular, NestJS, Payload CMS, Supabase}}{}
    \resumeItemListStart
        \resumeItem{Engineered 'GameBox', a full-stack monorepo for game center management, integrating a customer-facing web app with an admin CMS.}
        \resumeItem{Built a responsive frontend architecture using Angular, TypeScript, and SCSS.}
        \resumeItem{Developed a backend system using NestJS and Payload CMS, leveraging Supabase for secure authentication and real-time database operations.}
    \resumeItemListEnd

	\resumeSubheading {Malware Analyst Trainee}{Apr. 2025 -- Jun. 2025} {Bitdefender $|$ \emph{Java, Python, C, x86 Assembly, IDA Pro, jadx}}{}
    \resumeItemListStart
        \resumeItem{Conducted static and dynamic analysis of Windows and Android malware samples to identify command-and-control protocols and persistence mechanisms.}
        \resumeItem{Reverse engineered ransomware encryption routines using IDA Pro (x86 disassembly) and jadx (Java decompilation) to understand payload behavior.}
        \resumeItem{Investigated Android system vulnerabilities and exploitation techniques, analyzing APK structures and security models in sandboxed environments.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

    %-----------TECHNICAL SKILLS-----------
	\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{
		\textbf{Languages}{: C/C++, C\#, Python, Java, TypeScript, SQL, Bash} \\

		\textbf{High Performance Computing}{: MPI, OpenMP, POSIX Threads, SIMD, Shared Memory, Distributed Systems} \\

		\textbf{Systems and Tools}{: Linux, Docker, Jenkins, Git, Meson, CMake, Postman, IDA Pro, jadx, Wireshark} \\

		\textbf{Web Development}{: React, Angular, NestJS, ASP.NET Core, Hono} \\

		\textbf{Databases}{: PostgreSQL, Supabase, Entity Framework Core} \\

		\textbf{Data Analysis}{: NumPy, Pandas, Matplotlib, PyTorch, Power BI} \\

		\textbf{Spoken Languages}{: English (C1/Advanced), Romanian (Native)}
		}}
	\end{itemize}

	%-----------PROJECTS-----------
	\section{Projects}
	\resumeSubHeadingListStart

	\resumeProjectHeading
	{\textbf{Vibecodium - Collaborative Browser-Based IDE} $|$ \emph{React, Hono, Bun, Supabase, Docker, Vercel}}{Mar. 2026 -- Present}
	\resumeItemListStart
		\resumeItem{Won 1st Place in Web Development at the iTEC 2026 Hackathon.}
		\resumeItem{Built a collaborative browser-based IDE with real-time multi-user editing (Yjs CRDT).}
		\resumeItem{Integrated an AI coding assistant using Server-Sent Events (SSE) for real-time code generation and completion suggestions.}
		\resumeItem{Implemented a sandboxed Docker execution environment for running user-submitted code with isolated filesystem and network access.}
		\resumeItem{Integrated one-click Vercel deployment for user projects with automatic environment variable configuration and build pipeline orchestration.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{\href{https://github.com/paulhondola/Smart-Shopping-Assistant}{\underline{Smart Shopping Assistant}}} $|$ \emph{React, TypeScript, ASP.NET Core, PostgreSQL, OpenAI}}{Apr. 2026 -- Jun. 2026}
	\resumeItemListStart
		\resumeItem{Built a full-stack e-commerce platform with an AI-powered agentic cart analyzer, developed within the LigaAC Labs x NetRom industry mentorship program.}
		\resumeItem{Architected a sequential two-agent LLM pipeline that detects active and near-miss promotions and composes personalized product recommendations.}
		\resumeItem{Engineered a layered ASP.NET Core backend over PostgreSQL with Entity Framework Core and JWT role-based authentication.}
		\resumeItem{Kept a deterministic server-side promotion engine authoritative over the LLM to ensure pricing accuracy.}
		\resumeItem{Developed a responsive React 19 + TypeScript SPA (Vite, Material-UI, TanStack Query) consuming the REST API.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{ArchLens Analyzer} $|$ \emph{Python, Java, C\#, Reverse Engineering}}{Mar. 2026 -- Apr. 2026}
	\resumeItemListStart
		\resumeItem{Polyglot CLI tool (Python orchestrator + Java/C\# backends) that reverse-engineers compiled binaries (.jar, .dll) into UML class diagrams using runtime reflection.}
		\resumeItem{Outputs PlantUML and yUML; built with a layered pipeline architecture across a Maven and .NET monorepo.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{AtomC Compiler} $|$ \emph{C, Meson, Compiler Design}}{Mar. 2026 -- May. 2026}
	\resumeItemListStart
		\resumeItem{Developed a C-like language compiler frontend from scratch in C.}
		\resumeItem{Implemented a lexer, parser, and semantic analyzer to process and validate C source code.}
		\resumeItem{Established CI pipeline with integration test suites for lexer, parser, domain/type analyzer, stack-based virtual machine and code generator.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{Distributed Image Processing System} $|$ \emph{C, MPI, OpenMP, Meson, Python, Assembly}}{Dec. 2025 -- Jan. 2026}
	\resumeItemListStart
		\resumeItem{Implemented a high-performance hybrid parallel image processing engine utilizing MPI for distributed memory and OpenMP for shared memory parallelism.}
		\resumeItem{Engineered diverse parallel architectures including a standard multithreaded approach, distributed message passing, shared filesystem optimization, a producer-consumer task pool model and hybrid parallelism.}
		\resumeItem{Validated the efficiency of SIMD vectorization by inspecting generated assembly code across different compiler optimization levels.}
		\resumeItem{Optimized computationally intensive convolution kernels (Gaussian Blur, Ridge Detection) for processing large BMP images across cluster nodes.}
		\resumeItem{Developed an automated benchmarking suite with Python visualization to analyze strong scaling, speedup, and parallel efficiency.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{Parallel DMM Benchmark and Analysis} $|$ \emph{C, OpenMP, Meson, Python, Assembly}}{Oct. 2025 -- Nov. 2025}
	\resumeItemListStart
		\resumeItem{Developed a benchmarking suite for dense matrix multiplication, implementing serial and parallel algorithms with OpenMP.}
		\resumeItem{Implemented loop permutations and cache blocking (tiling) strategies to optimize memory access patterns and minimize cache misses.}
	\resumeItemListEnd

	\resumeSubheading{Deepblue Maker - Underwater Robotics Summer Camp}{Jul. 2025 -- Aug. 2025}{Hangzhou Dianzi University, China}{}
    \resumeItemListStart
        \resumeItem{Co-engineered a remotely operated underwater vehicle (ROV) capable of environmental mapping and real-time object detection.}
        \resumeItem{Mechanical: Designed and 3D-printed a custom water-sealed chassis using SolidWorks; validated buoyancy and structural integrity through physical testing.}
        \resumeItem{Embedded Systems: Programmed an STM32 microcontroller for precise thruster propulsion control and hardware interfacing.}
        \resumeItem{Computer Vision: Deployed a YOLO-based object detection model on a Raspberry Pi 5 to identify sea life from live camera feeds.}
    \resumeItemListEnd

	\resumeSubHeadingListEnd
	%-----------CERTIFICATES-----------
	%----------------------------------

	%-------------------------------------------
\end{document}
